Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-15 paper_comparison/paper_comparison/paper_comparison.tex
update distribution cmp

\hypertarget{distribution-of-regressor}{%
\subsection{Distribution of regressor}\label{distribution-of-regressor}}

The impact of the distribution of \(X_raw\) on the power is displayed in
Figure \ref{fig:dist-power}. The power curve of F-test is stable across
different distributions, while the visual test has a steeper power curve
for normal and uniform distribution. BP-test performs worse for discrete
uniform distribution and uniform distribution but has relatively high
power for normal distribution. SW-test outperforms BP-test for discrete
uniform distribution but remains as the worst test for other
distributions. The results indicate those inappropriate residual-based
tests are sensitive to the distribution of the regressor.

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/dist-power-1}

@@

\caption{...}\label{fig:dist-power}
\end{figure}

--\textgreater{}

--\textgreater{}

>>>>

The impact of the distribution of \(X_{raw}\) on the power is displayed
in Figure \ref{fig:dist-power}. For the non-linearity model, the power
curve of F-test is stable across different distributions, while the
visual test has a more gentle power curve for the discrete uniform
distribution as it contains lineups with larger effect size. BP test
performs worse for discrete uniform distribution but has relatively high
power for normal distribution. SW test outperforms BP test for discrete
uniform distribution but remains as the worst test for other
distributions. The results indicate those inappropriate residual-based
tests are sensitive to the distribution of the regressor.

For the heteroskedasticity model, F-test is entirely insensitive to the
non-constant variance. The visual test has similar power as the SW
test\\
for normal distribution and lognormal distribution, and has higher power
for uniform distribution, and lower power for discrete uniform
distribution.

But still, we observe the huge gap in power between the preferred
conventional tests and the visual test which is consistent with our
previous argument that conventional test is too sensitive for diagnosing
non-linearity and heteroskedasticity.

@@

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-8-1}

@@

\caption{...}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1} \end{center}
